Understanding the impacts of video-guided activities on parent-child interaction

### 2019-10-03 paper/manuscript.Rmd
cleaned transcripts, rewrote discussion

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4576"

@@

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"
load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting

e1ld <- d %>%
  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         parent_ed = as.numeric(langcog::scale(parent_ed, scale=T)),
         gender = as.factor(gender),
         video = as.factor(video))

@@

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))

@@

e2_gender = table(d$gender)
e2_ethnicity = table(d$ethnicity)
e2_parent_ed = table(d$parent_ed)
e2_12to18 = nrow(subset(d, age<1.5))
e2_18to24 = nrow(subset(d, age>=1.5))
```

@@

## Results

@@

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
summary(modTTR) 
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11

modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
summary(modMTLD) 
e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -9.19

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 59.41

@@

```{r, e1ld-exploratory, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
# only 54 parents completed the EPAQ
modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
summary(modTTRE) #

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
There was significantly lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]). 
A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
There were significantly more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.

@@

## Discussion

@@

As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% confidence intervals: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other significant effects on parental bids for JA.

@@

```{r meta-analysis, include=F}

# Discussion

This study investigated whether and how digital parenting advice alters parents' interactions with their toddlers during a 3-minute play period.
In Experiment 1, parents of 6--24-month-olds made more bids for JA after watching the activity video as compared to no video, which was also found in the parents of 12--24-month-olds in Experiment 2 in comparison to a science video control.
Experiment 2 moreover found fewer JA episodes for parents of older infants after a science video, while parents of older children engaged in more JA after the activity video.
In combination, these results suggest that short parenting messages suggesting activities can encourage parents to make more attempts to engage their child in joint attention, and that in some cases--especially in older children--these bids are successful in increasing engagement.

Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp. 1). However, activity videos resulted in parents using more word tokens (significant in Exp. 1; numerical in Exp. 2), while the number of word types did not differ significantly across conditions.
Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens.
Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity.
Indeed, the words identified by the corpus analysis as being words most characteristic of the activity videos were related to requests (e.g., "give", "put", "take"), whereas words characteristic of the control conditions were more invitational (e.g., "say", "let", "like").

In sum, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term. 
Future studies should investigate whether these changes in parents' speech and attempts to engage their children persist after the treatment. 
Another target for future study is to determine whether, over a longer treatment period, children begin to respond to the increased bids for joint attention and greater number of tokens by engaging more with their parent, and perhaps even beginning to play differently.

>>>>

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4706"

@@

```{r load-exp1-lexical-data, include=F}
e1path = "../parenting_obs_e1/"
#load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))

d$MTLD = d$MTLD2
d$TTR = d$TTR2
d$types = d$types2
d$tokens = d$tokens2

e1ld <- d %>%
  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD2),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         parent_ed = as.numeric(langcog::scale(parent_ed, scale=T)),
         gender = as.factor(gender),
         video = as.factor(video))

@@

```{r load-exp2-lexical-data, echo=F}
e2path = "../parenting_obs_e2/"
#load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))

d <- read.csv(paste(e2path,"exp2_conditions2.csv",sep=''))
d$MTLD = d$MTLD2
d$TTR = d$TTR2
d$types = d$types2
d$tokens = d$tokens2

@@

e2_gender = table(d$gender)
e2_ethnicity = table(d$ethnicity)
e2_parent_ed = table(d$parent_ed)
e2_12to18 = nrow(subset(d, age<1.5)) # wrong now that age is scaled
e2_18to24 = nrow(subset(d, age>=1.5))
```

@@

## Results and Discussion

@@

modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
summary(modTTR) 
e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.10

modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
summary(modMTLD) 
e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -6.27

# predict word tokens
tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
summary(tokens_mod)
e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 57.1

@@

```{r, e1ld-exploratory, echo=F, include=F}
# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
# only 54 parents completed the EPAQ
modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
summary(modTTRE) # conditionexp, RR, genderM, parent_ed 
get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]). 
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no predicted influence of age.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
There were more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no predicted effects on the number of or total duration of coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, only the regression predicting the number of passive JA episodes showed an effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.

@@

### Discussion

@@

We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% confidence intervals: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other significant effects on parental bids for JA.

@@

# General Discussion

We were interested in how digital parenting advice alters parents' interactions with their children. 
We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions. 
Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention. 
In two experiments, we found that activity videos increased parent bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
In some cases--especially in older children--these bids were successful in increasing engagement. 
We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity). 
Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., "give", "put", "take") whereas control conditions featured more invitational words (e.g., "say", "let", "like").

The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions. 
Why were they successful? 
When parents are asked to play with their children in the presence of new toys, they may choose to follow their child's lead and engage in free play.
While free play is positive, it nevertheless results in less scaffolded activity than when parents are given a goal that suggests a repertoire of ways to guide their child. 
Parents may also persist in providing opportunities for their child to complete the activity, leading to more repetitive language but also more offers of engagement.

Our study has a number of limitations related to design and sample, each of which suggests possible future directions. 
First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned). 
A longer-term study would also be able to measure whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
Second, our design assumes that parents have access not only to activities but also to the materials to complete them; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions. 
Providing materials may be critical for the success of activity suggestions. 
Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research. 
A key goal for future research is to assess the generality of these findings across populations.

<!-- Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity. -->

<!-- Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp. 1). However, activity videos resulted in parents using more word tokens (significant in Exp. 1; numerical in Exp. 2), while the number of word types did not differ significantly across conditions. -->
<!-- Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens. -->

In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.

### 2019-10-03 paper/manuscript.tex
cleaned transcripts, rewrote discussion

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
There was significantly lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.30, 95\% CI={[}-15.37,-3.18{]}), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 59.07, 95\% CI={[}19.58,97.44{]}), with parents using more words in the Activity Video condition (mean: 225, bootstrapped 95\% confidence intervals: {[}199,252{]}) than in the No Video condition (mean: 165, bootstrapped 95\% confidence intervals: {[}139,193{]}).

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

@@

84 infants (F = 36, M = 46) aged 12-24 months (41 12-17.9 month-olds, 43 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent.
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
Sixteen parents reported their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).

@@

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

@@

As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% confidence intervals: 11.79, 14.24; \(\beta=3.07\), 95\% CI = {[}1.15,5.06{]}) than after the Science Video (mean: 9.89, 95\% CI: {[}8.73, 11.10{]}).
There were no other significant effects on parental bids for JA.

@@

\hypertarget{discussion-1}{%
\section{Discussion}\label{discussion-1}}

This study investigated whether and how digital parenting advice alters parents' interactions with their toddlers during a 3-minute play period.
In Experiment 1, parents of 6--24-month-olds made more bids for JA after watching the activity video as compared to no video, which was also found in the parents of 12--24-month-olds in Experiment 2 in comparison to a science video control.
Experiment 2 moreover found fewer JA episodes for parents of older infants after a science video, while parents of older children engaged in more JA after the activity video.
In combination, these results suggest that short parenting messages suggesting activities can encourage parents to make more attempts to engage their child in joint attention, and that in some cases--especially in older children--these bids are successful in increasing engagement.

Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp. 1). However, activity videos resulted in parents using more word tokens (significant in Exp. 1; numerical in Exp. 2), while the number of word types did not differ significantly across conditions.
Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens.
Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity.
Indeed, the words identified by the corpus analysis as being words most characteristic of the activity videos were related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}), whereas words characteristic of the control conditions were more invitational (e.g., \enquote{say}, \enquote{let}, \enquote{like}).

In sum, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
Future studies should investigate whether these changes in parents' speech and attempts to engage their children persist after the treatment.
Another target for future study is to determine whether, over a longer treatment period, children begin to respond to the increased bids for joint attention and greater number of tokens by engaging more with their parent, and perhaps even beginning to play differently.

>>>>

\hypertarget{results-and-discussion}{%
\subsection{Results and Discussion}\label{results-and-discussion}}

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
There was significantly lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.42, \(\beta=\)-0.10, 95\% CI={[}-0.15,-0.05{]}).
A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 16.81) than in the No Video condition (mean: 23.04, \(\beta=\)-6.27, 95\% CI={[}-11.54,-1.03{]}), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 56.94, 95\% CI={[}17.67,95.19{]}), with parents using more words in the Activity Video condition (mean: 228, bootstrapped 95\% confidence intervals: {[}199,252{]}) than in the No Video condition (mean: 169, bootstrapped 95\% confidence intervals: {[}139,193{]}).

@@

\hypertarget{discussion}{%
\subsubsection{Discussion}\label{discussion}}

@@

84 infants (F = 36, M = 46) aged 12-24 months (84 12-17.9 month-olds, 0 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent.
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
Sixteen parents reported their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 2), four-year college (n = 36), some graduate school (n = NA), to completed graduate school (n = NA) or declined to state (n = 13).

@@

\hypertarget{results-and-discussion-1}{%
\subsection{Results and Discussion}\label{results-and-discussion-1}}

@@

We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% confidence intervals: 11.79, 14.24; \(\beta=3.07\), 95\% CI = {[}1.15,5.06{]}) than after the Science Video (mean: 9.89, 95\% CI: {[}8.73, 11.10{]}).
There were no other significant effects on parental bids for JA.

@@

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

We were interested in how digital parenting advice alters parents' interactions with their children.
We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions.
Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
In two experiments, we found that activity videos increased parent bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2).
In some cases--especially in older children--these bids were successful in increasing engagement.
We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}) whereas control conditions featured more invitational words (e.g., \enquote{say}, \enquote{let}, \enquote{like}).

The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions.
Why were they successful?
When parents are asked to play with their children in the presence of new toys, they may choose to follow their child's lead and engage in free play.
While free play is positive, it nevertheless results in less scaffolded activity than when parents are given a goal that suggests a repertoire of ways to guide their child.
Parents may also persist in providing opportunities for their child to complete the activity, leading to more repetitive language but also more offers of engagement.

Our study has a number of limitations related to design and sample, each of which suggests possible future directions.
First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned).
A longer-term study would also be able to measure whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
Second, our design assumes that parents have access not only to activities but also to the materials to complete them; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions.
Providing materials may be critical for the success of activity suggestions.
Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research.
A key goal for future research is to assess the generality of these findings across populations.

In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.
